Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-05-19 paper.tex
adding synthetic workflow app
small change
synth wf desc

>>>>

\section{Synthetic Workflow Performance Evaluation}
We use a synthetic application consisting of
various computation and memory intensive tasks. The computation intensive task
is matrix multiplication while the memory intensive tasks are array summation,
scale, and triad operations from the stream benchmarks~\cite{Stream}.  The
graph shown in Figure~\ref{fig:synthetic} shows the overall data flow of
synthetic workflow.

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=8cm]{figures/synthetic_combine.png}
\caption{The synthetic workflow representation}
\label{fig:synthetic}
\end{center}
\end{figure}

\subsection{calibration}
